\textbf{NBA Party}

### 2017-05-09 poster/poster.tex
Formatting to ensure everything fits on one page.

\block{Idea} {     It's not unreasonable to think that game performance can be affected (in part) by what takes place off the court. We are interested to see if teams exhibit a decline in performance the day following a game in a party city. We exploit data on bookmaker spreads, the expected score differential between two teams after conditioning on observable performance. We expect a team to meet the spread half the time, since this is how bookmakers minimize risk on their end. We construct a model which attempts to estimate the causal effect of  visiting a "party-city" the day before a game on the probability of meeting the spread. }

\block{Model}{
  \[
    \texttt{meet spread} \sim \texttt{party} + \substack{\texttt{days since} \\ \texttt{last game}} + \substack{\texttt{time}\\ \texttt{difference}} + \substack{\texttt{distance} \\ \texttt{traveled}}
  \]
  Our setup relies on a quasi-experiment: we look for instances where a team plays in a city
  with active nightlife, then plays a game in a different location the next day. Since next-day
  opponent is uncorrelated with exposure to treatment, we have identification in our variable of 
  interest.
}

@@

\begin{columns}     \column{0.5}     \block{Profits on MLB Betting in 2016}     {         \begin{tikzfigure}             \includegraphics[width=0.4\textwidth]{figures/mlb_bets}         \end{tikzfigure}     }     \column{0.5}     \block{Description of the figure}{
      On the left, we plot profits as a function of time over the 2016 season. For each relevant
      game, we place a bet if our model instructs us of odds sufficiently different from what
      the betting house suggests. We account for the bookmaker's cut. In the early season,
      at its worst we are out of pocket \$750 dollars. By season end, we have recouped all of
      our initial investment plus an additional \$13.5k.
    }

>>>>

\block{~} {     It's not unreasonable to think that game performance can be affected (in part) by what takes place off the court. We are interested to see if teams exhibit a decline in performance the day following a game in a city with active nightlife. 
We exploit data on bookmaker spreads, the expected score differential between two teams after conditioning on observable performance. We expect a team to meet the spread half the time, since this is how bookmakers minimize risk on their end. We construct a model which attempts to estimate the causal effect of  visiting a "party-city" on subsequent day performance as measured by the spread. Since next-day
  opponent is uncorrelated with exposure to treatment, we have identification in our variable of 
  interest.
}

\block{Model}{
  \[
    \texttt{meet spread} \sim \texttt{party} + \substack{\texttt{days since} \\ \texttt{last game}} + \substack{\texttt{time}\\ \texttt{difference}} + \substack{\texttt{distance} \\ \texttt{traveled}}
  \]
}

@@

\begin{columns}     \column{0.5}     \block{Profits on MLB Betting in 2016}     {         \begin{tikzfigure}             \includegraphics[width=0.4\textwidth]{figures/mlb_bets}         \end{tikzfigure}     }     \column{0.5}     \block{Description of the figure}{
      On the left, we plot profits as a function of time over the 2016 season. For each relevant
      game, we place a bet if our model instructs us of odds sufficiently different from what
      the betting house suggests. We account for the bookmaker's cut. In the early season,
      at its worst we are out of pocket \$750 dollars. By season end, we have recouped all of
      our initial investment plus an additional \$11.5k.
    }
